Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-14 paper/main.tex
revise discussion of individual results

\begin{itemize}
\item lateral occipital cortex: 4 contrasts (all bilateral)
\end{itemize}

@@

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Similarly to previous studies that used small sets of experimentally controlled
stimuli, we also used GLMs to investigate hemodynamic brain activity during two
naturalistic stimuli.
% more than just one contrast
For both naturalistic stimuli, we computed several $t$-contrasts that differed
in the contrasted categories of stimulus features and the amount of available
data to test the robustness of our findings.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a visual localizer experiment
done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' is correlated with increased activation in the
anterior PPA of both hemispheres.
% to do
Other possible ``honourable'' mentions (here? and in the following discussion?)
\begin{itemize}
    \item RSC
    \item what could be LOC / OPA
    \item AV; should (shortly) be discussed
    \item robustness (imo shortly discussed; it is about robustness not about
        how all contrasts are different in detail and how results differ in
        detail; yes, totally interesting but out of scope
    \item discuss negative contrasts?
\end{itemize}

@@

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
%
As a results, stimulus features that we annotated to create the regressors could
have been correlated leading to shared variance that lowers detection power.
% computing the correlations
Hence, we first tested for correlation of regressors within and across both
naturalistic stimuli (s. Figure \ref{fig:reg-corr})
% results of computing feature correlation
Results show no to minor correlations of regressors with regressors of the same
stimulus.
% encouraged by that we build contrasts (statement)
Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used conceptualized stimuli.

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements\todo{should
already be mentioned in disc. of primary contrasts}
% AO: auditory cortices
Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
categories (cf. contrasts 2, 3, 6, 7) show significant clusters in (primary and
secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

\todo[inline]{check location in primary contrast and overlap across contrasts}

\todo[inline]{report numbers of contrast in AO \& AV that show sign. clusters in
RSC}

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrasts of both stimuli in the retrosplenial cortex (RSC).
% location functionally defined
As a scene-responsive region, the RSC is functionally defined and not
necessarily identical to the anatomically defined retrosplenial cortex [26]
\citep{epstein2008parahippocampal}.
% function
The RSC is strongly active during scene viewing, scene imagery [25] and mental
imagination of navigation through familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
The RSC is located in the retrosplenial cortex, and posterior cingulate region,
near to the point where the calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.
% anatomy of real RSC
The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
the posterior cingulate (BA 23 and 31) [51–56]
\citep{epstein2008parahippocampal}.

% discussion of what the RSC does
interpretation cf.: \citep{vann2009what, chrastil2018heterogeneity,
silson2019posterior}
% conclusion

% baldassano2016two
\citep{baldassano2016two}: RSC appears to be most directly involved in orienting
the viewer to the structure of the environment (both within and beyond the
borders of the presented image) for the purpose of navigational planning; it
encodes both absolute location and facing direction [Vass and Epstein, 2013;
Epstein and Vass, 2014; Marchette et al., 2014], integrates across views
presented in a panoramic sequence [Park and Chun, 2009], and shows strong
familiarity effects [Epstein et al., 2007a,b] \citep{baldassano2016two}.

@@

\begin{itemize}

\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
Perception \item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
and Selectively Involved in Scene Perception \item Nasr (2011). Scene-selective
    cortical regions in human and nonhuman primates \item Dilks (2011).
    Mirror-image sensitivity and invariance in object \& scene processing \item
    MacEvoy and Epstein (2007). Position selectivity in scene- and
object-responsive \item Grill-Spector (2003). The neural basis of object
    perception \item Hasson (2003). Large-scale mirror-symmetry organization
    \item Nakamura (2000). Functional delineation of the human occipito-temporal
        areas \end{itemize}

%
\citep{baldassano2016two} regarding functional difference pPPA vs. OPA: The
functional distinction between pPPA and OPA is currently unclear. Previous work
has speculated about the purpose of the apparent ventral and dorsal
``duplication'' of regions sensitive to large landmarks, proposing that it may
be related to different output goals (e.g., action planning in OPA, object
recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
connections (e.g., lower visual field processing in OPA, upper visual field
processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
also use information from different visual eccentricities: OPA processing less
peripheral, relatively high-resolution environmental features. pPPA processing
more peripheral, large-scale geometry, and context [Baldassano et al., 2016a]
\citep{baldassano2016two}.

@@

An examination of these results on an individual participant basis reveals that
this pattern remains highly reliable and, therefore, does not appear to be a
by-product of group averaging across slightly offset discrete functional
subregions[aminoff2015associative].

\subsubsection{AO stimulus}

\todo[inline]{how to discuss Bland-Altman-Plots? Let's talk about that
shortly please}

\todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
    in the AO contrast than in the contrast of the visual localizer -> should
    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
    the significant cluster of the AO contrast}

% intro
In order to test the audio-description's performance as a functional localizers,
we also compared the results of the audio-description's primary contrast to
results of the dedicated visualizer on the level of individual subjects.
% results of dedicated localizer
The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
12 of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
a unilateral significant cluster in one subject.
% conclusion
Results of our exploratory analyses suggest that a naturalistic auditory
stimulus is suitable to localize (the anterior part) of a higher-level visual
area in the majority of subjects.

% one threshold for all
Here we used a ``one threshold fits all approach`` whereas
\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
subject's unthresholded $z$-maps by visual judgment and the ``best fitting''
threshold.
% one contrast for all
Moreover, we chose the same contrast to look at individual results of all
subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

% quote from Hanke (2014)
\citep{hanke2014audiomovie}: Compared to AV stimulus, the AO stimulus leaves a
much larger margin for inter-individual differences in imagining scenery, as
well as actors' character and personality traits, while still preserving the
time-locked presentation of information to a listener. At the same time, the AO
stimulus limits the effect of an attentional focus on the selection of a subset
of simultaneously occurring auditory events, in contrast to the selection of
different parts of the visual field.

@@

\todo[inline]{was not aim of the study; AV ROIs are in the plot of individual
    slices but not in the Bland-Altman-Plots}

@@

\subsubsection{pros \& cons of natural stimuli (esp. narrative) as localizer}

>>>>

\begin{itemize}
    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
\end{itemize}

@@

\todo[inline]{convey better that we do not have lots of ``random clusters''}

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Similarly to previous studies that used small sets of experimentally controlled
stimuli, we also used GLMs to investigate hemodynamic brain activity during two
naturalistic stimuli.
% more than just one contrast
For both naturalistic stimuli, we computed several $t$-contrasts that differed
in the contrasted categories of stimulus features and the amount of available
data to test the robustness of our findings.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a visual localizer experiment
done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' is correlated with increased activation in the
anterior PPA of both hemispheres.

% to do
\todo[inline]{Other possible ``honourable'' mentions; here (?), and in the
following discussion?}

\begin{itemize}
    \item RSC
    \item what could be LOC / OPA
    \item AV; should (shortly) be discussed
    \item robustness (imo shortly discussed; it is about robustness not about
        how all contrasts are different in detail and how results differ in
        detail; yes, totally interesting but out of scope
    \item discuss negative contrasts?
\end{itemize}

@@

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
%
As a results, stimulus features that we annotated to create the regressors could
have been correlated leading to shared variance that lowers detection power.
% computing the correlations
Hence, we first tested for correlation of regressors within and across both
naturalistic stimuli (s. Figure \ref{fig:reg-corr})
% results of computing feature correlation
Results reveal no to minor correlations of regressors with regressors of the
same stimulus.
% encouraged by that we build contrasts (statement)
Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used conceptualized stimuli.

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements\todo{could
    already already be mentioned in discussion of primary contrasts}
% AO: auditory cortices
Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
categories (cf. contrasts 2, 3, 6, 7) show significant clusters in (primary and
secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% but RSC
Apart from the PPA, we find significantly increased activity in the
retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AO
stimulus: 7 contrasts; AV stimulus: 3 contrasts).
% location functionally defined
The RSC as a scene-selective region is not necessarily spatially congruent with
the anatomically defined retrosplenial cortex [26] (BA 29 and 30)
\citep{epstein2008parahippocampal} but functionally defined as the posterior
medial region that exhibits increased hemodynamic activity to visual scenes and
during mental imagination trough familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
This functionally defined RSC is located in the retrosplenial cortex, and
posterior cingulate region (BA 23 and 31) [51–56], near to the point where the
calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.

% discussion of what the RSC does
interpretation cf.:
\begin{itemize}
    \item \citep{chrastil2018heterogeneity}
    \item \citep{vann2009what}
    \item \citep{silson2019posterior}
    \item \citep{baldassano2016two}: RSC appears to be most directly involved in orienting the viewer to the structure of the environment (both within and beyond the borders of the presented image) for the purpose of navigational planning; it encodes both absolute location and facing direction [Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014], integrates across views presented in a panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects [Epstein et al., 2007a,b].
\end{itemize}

@@

\begin{itemize}
\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
    Perception
\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
    Selectively Involved in Scene Perception
\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
    primates
\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
    processing
\item MacEvoy and Epstein (2007). Position selectivity in scene- and
    object-responsive
\item Grill-Spector (2003). The neural basis of object perception
\item Hasson (2003). Large-scale mirror-symmetry organization
\item Nakamura (2000). Functional delineation of the human occipito-temporal
    areas
\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
    The functional distinction is unclear.
    Previous work has speculated about the purpose of the apparent ventral and
    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
    that it may be related to different output goals (e.g., action planning in
    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
    different input connections (e.g., lower visual field processing in OPA,
    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
    2015].
    OPA and pPPA may also use information from different visual
    eccentricities: OPA processing less peripheral, relatively high-resolution
    environmental features. pPPA processing more peripheral, large-scale
    geometry, and context [Baldassano et al., 2016a]
\end{itemize}

@@

\todo[inline]{how to discuss Bland-Altman-Plots???}

\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
    PPA are higher in AO contrasts than in contrast of localizer}

% intro
To test if an auditory narrative could substitute a visual localizer experiment,
we also examined the results of the primary AO contrast on the level of
individual subjects.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
unilateral significant cluster in one subject.
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
% group vs individual
Results on an inidividual level reveal that significant cluster are located in
the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
a group level is not just a by-product of the averaging process but can reliably
be found in individual study participants.
% conclusion
Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
is in principle suitable to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

@@

\todo[inline]{was not aim of study; results of primary AV contrasts are in plots
    if individual; Bland-Altman-Plots focus on primary AO contrast alone}

@@

\subsubsection{zpros \& cons of natural stimuli (esp. narrative) as localizer}

% quote from Hanke (2014)
\citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
inter-individual differences in imagining scenery.  The AO stimulus limits the
effect of an attentional focus on the selection of a subset of simultaneously
occurring auditory events, in contrast to the selection of different parts of
the visual field.
